Intentional release of native species undermines ecological stability

### 2022-09-27 rmd/supporting_info.Rmd
Update supporting_info.Rmd
rmd

Parameter values used in the main and sensitivity analysis. Five hundred parameter values were drawn randomly from uniform distributions in the sensitivity analysis.

@@

Median estimates of the Bayesian state-space model. Numbers in parenthesis indicate 95% credible intervals. Site-specific parameters were excluded due to a large number of parameters.

@@

knitr::kable(df_ssm,
             align = c(rep("l", 3), "c"),
             format = "markdown")

@@

                       "\n```{r figure_s", i + j,", fig.width = 9.5, fig.height = 8}
                       \n\n
                       list_g_theory[[",i,"]]
                       \n\n
                       ```\n",

@@

c_text <- c("whole community",
            "masu salmon",
            "unenhanced species")

>>>>

Parameter values used in the whole community simulation.

@@

Median estimates of the Bayesian state-space model. Site-specific parameters were excluded due to a large number of parameters.

@@

knitr::kable(df_ssm,
             align = c(rep("l", 2), rep("c", 2)),
             format = "markdown")

@@

                       "\n```{r figure_s", i + j,", fig.width = 10, fig.height = 7}
                       \n\n
                       list_g_theory[[",i,"]]
                       \n\n
                       ```\n",

@@

c_text <- tibble(Group) %>% 
  mutate(text = case_when(Group == "all" ~ "whole community",
                          Group == "masu_salmon" ~ "masu salmon",
                          Group == "other" ~ "unenhanced species")) %>% 
  pull(text)
